Topological Equivariant Artist Model

### 2022-03-29 slides/main.tex
artist nts

\begin{frame}<presentation:1-|handout:1>
    \frametitle{Functor $\textcolor{functor}{\bm{F}}: \textcolor{source}{\mathcal{C}} \rightarrow \textcolor{target}{\mathcal{D}}$}
\begin{columns}
    \column{.39\textwidth}
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement = \&, ]
            \onslide*<1-|handout:1>{\textcolor{source}{c}} 
            \onslide*<1-|handout:1>{\arrow[d, "f"', shift right=0, color=source]} 
            \onslide*<3-|handout:1>{\arrow[r, "F", color=functor, maps to]} \& 
            \onslide*<2-3|handout:0>{\textcolor{target}{d}}
            \onslide*<4-|handout:0>{\textcolor{target}{F(c)}} 
            \onslide*<0|handout:1>{\textcolor{target}{F(c)=d}} 
            \onslide*<2|handout:0>{\arrow[d, shift right=0, color=target]}
            \onslide*<3-|handout:0>{\arrow[d, "F(f)", shift right=0, color=target]}
            \onslide*<0|handout:1>{\arrow[d, "F(f)", shift right=3, color=target]} \\
            \onslide*<1-|handout:1>{\textcolor{source}{c^{\prime}}} 
            \onslide*<3-|handout:1>{\arrow[r, "F"', color=functor, maps to]}\& 
            \onslide*<2-3|handout:0>{\textcolor{target}{d^{\prime}}}
            \onslide*<4-|handout:0>{\textcolor{target}{F(c^{\prime})}}
            \onslide*<0|handout:1>{\textcolor{target}{F(c^{\prime})= d^{\prime}}}                    
        \end{tikzcd}
    \end{equation*}
    \column{.59\textwidth}
    \begin{alertblock}<5-|handout:1>{composition}
        \begin{align*}
            \textcolor{functor}{F}(\textcolor{source}{g}) \circ  \textcolor{functor}{F}(\textcolor{source}{f}) = \textcolor{functor}{F} (\textcolor{source}{g}\circ \textcolor{source}{f})
        \end{align*}
    \end{alertblock}
    \begin{alertblock}<6-|handout:1>{identity}
        \begin{align*}
            \textcolor{functor}{F}(\textcolor{source}{id_c}) = \textcolor{target}{id}_{\textcolor{functor}{F}(\textcolor{source}{c})}
        \end{align*}
    \end{alertblock}
\end{columns}
\end{frame}

\subsubsection{Natural Transforms}
\begin{frame}<presentation:1-|handout:1>
    \frametitle{Natural Transformation $\textcolor{nattran}{\alpha}: \textcolor{functor}{F} \textcolor{nattran}{\Rightarrow} \textcolor{functor}{G}$}
    \adjustbox{scale=3, center}{
        \begin{tikzcd}[ampersand replacement=\&]
            \& {} \arrow[dd, "\alpha" , Rightarrow, shorten=1.5em, color=nattran] \&             \\
          \textcolor{source}{\mathcal{C}} \arrow[rr, "F", bend left, color=functor] \arrow[rr, "G"', bend right, color=functor] \& \& \textcolor{target}{\mathcal{D}} \\
            \& {} \&            
          \end{tikzcd}}
\end{frame}

\begin{frame}<presentation:1-|handout:1>
    \frametitle{Natural Transformation $\textcolor{nattran}{\alpha}: \textcolor{functor}{F} \textcolor{nattran}{\Rightarrow} \textcolor{functor}{G}$}
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement=\&]  
                \&  \& 
                \textcolor{target}{d_s} \& 
                \textcolor{source}{c} 
                \arrow[r, "G", maps to, color=functor] 
                \arrow[l, "F"', maps to, color=functor] \& 
                \textcolor{target}{d_t} \\
                \textcolor{source}{c_1} 
                \arrow[dd, "f" description, color=source] \& \& 
                \textcolor{target}{F(c_1)} 
                \arrow[dd, "F(f)"', color=target] 
                \arrow[rr, "\alpha_{c_1}", color=nattran] \& \& 
                \textcolor{target}{G(c_1)} 
                \arrow[dd, "G(f)", color=target] \\
                \& \& {} 
                \arrow[rr, "\alpha_{f}", dotted, color=nattran] \& \& {} \\
                \textcolor{source}{c_2} \& \& 
                \textcolor{target}{F(c_2)} 
                \arrow[rr, "\alpha{c_2}", color=nattran] \& \& 
                \textcolor{target}{G(c_2)} \\
                \& \& 
                \textcolor{target}{F} 
                \arrow[rr, "\alpha", Rightarrow, color=nattran] \& \& 
                \textcolor{target}{G}                        
        \end{tikzcd}                    
    \end{equation*}
\end{frame}

@@

\begin{frame}<presentation:1-|handout:1>
    \frametitle{Presheaf: $\sheafc: \mathcal{C}^{op} \textcolor{sheaf}{\rightarrow} \setc $}
    \begin{columns}
    \column{0.29\textwidth}
    \begin{tikzcd}[ampersand replacement=\&, row sep=huge]
        \onslide*<9-|handout:1->{\dfiberc}
        \onslide*<9-|handout:1->{\arrow[r, hook]} \& 
        \onslide*<1-|handout:1->{\dtotalc}
        \onslide*<1-|handout:1->{\arrow[d, "\pi"']} \\
           \& 
        \onslide*<1-|handout:1->{\dbasec}
        \onslide*<3-|handout:1->{\arrow[u, "\dsectionc \in \cgamma{\dbasec}{\dtotalc}"', bend right, pos=.5]}
        \end{tikzcd}
    \column{0.69\textwidth}
        \begin{tikzcd}[ampersand replacement = \&, column sep=small]
            \onslide*<3,6-|handout:0>{{\cgamma{\opensetc_1}{\dtotalc\restriction_{{\opensetc_1}}}}} 
            \onslide*<4-5|handout:0>{{\cgamma{\opensetc_1}{\dtotalc\restriction_{{\opensetc_1}}}}\in Ob(\setc)}
            \onslide*<0|handout:1>{\Ob(\setc) \ni {\cgamma{\opensetc_1}{\dtotalc\restriction_{{\opensetc_1}}}}}
            \&  
            {} \& 
            \onslide*<6-|handout:1>{{\cgamma{\opensetc_2}{\dtotalc\restriction_{\opensetc_2}}}} 
            \onslide*<7-|handout:1>{\arrow[ll, "\iota^*"', hook', color=set]} \\\& \&\\
            \onslide*<3|handout:0>{\opensetc_1 \subset \dbasec}
            \onslide*<4-5|handout:0>{\opensetc_1 \in Ob(\mathcal{\dbasec}^{\textcolor{base}{op}})}
            \onslide*<6-|handout:0>{\opensetc_1}
            \onslide*<0|handout:1>{Ob(\mathcal{\dbasec}^{\textcolor{base}{op}}) \ni \opensetc_1} 
            \onslide*<5-|handout:0>{\arrow[uu, "\sheafc_{\dbasec, \dtotalc}", maps to, color=sheaf]}
            \onslide*<0|handout:1>{\arrow[uu, "\sheafc_{\dbasec, \dtotalc}", maps to, color=sheaf, shift right = 10]}
            \onslide*<7-|handout:1>{\arrow[rr, "\iota"', hook, color=base]} \&   
            \onslide*<8-|handout:1>{\arrow[uu, "\sheafc_{\dbasec, \dtotalc}" description, maps to, color=sheaf]} \& 
            \onslide*<6-|handout:1>{\opensetc_2} 
            \onslide*<6-|handout:1>{\arrow[uu, "\sheafc_{\dbasec, \dtotalc}"', maps to, color=sheaf]}                   
            \end{tikzcd}
    \end{columns}
    \begin{center}
        \begin{alertblock}<8-|handout:1>{stalk}
            \begin{align*}
                \sheafc_{\dbasec, \dtotalc}\restriction_{\dbasepointc}\coloneqq \lim\limits_{\opensetc\ni \dbasepointc} \Gamma(\opensetc, \dtotalc\restriction_{\opensetc}) \\
                 \dfiberc_{\dbasepointc} \subset  \sheafc_{\dbasec, \dtotalc}\restriction_{\dbasepointc}
            \end{align*}
        \end{alertblock}

        \begin{alertblock}<9-|handout:1>{germ}
            %germ  is tau at limit, \tau(k) \in germ
            \begin{align*}
                \dsectionc(\dbasepointc) \in \sheafc_{\dbasec, \dtotalc}\restriction_{\dbasepointc}
            \end{align*}
        \end{alertblock}
    \end{center}
\end{frame}

\begin{frame}<presentation:1|handout:1>{Sheaves on Bundles}
    A sheaf is a presheaf that satisfies the following two axioms\cite{bakerMathsSheaf}\\
    \begin{block}<2-|handout:1>{locality}
        \onslide<3-|handout:1>{
        given $\opensetc = \bigcup\limits_{i\in I} \opensetc_i$ and $\dsectionc^{a}, \dsectionc^{b} \in \sheafc(\opensetc)$,}
        \onslide<4|handout:1>{\\
        if $\dsectionc^{a}\restriction_{\opensetc_i} = \dsectionc^{b}\restriction_{\opensetc_i}$ for each $\opensetc_i \in \opensetc$}
        \onslide<4|handout:1>{then $\dsectionc^{a} = \dsectionc^{b}$}
    \end{block} 
    \begin{block}<5-|handout:1>{gluing} 
         given $\dsectionc^{i} \in \sheafc(\opensetc_i)$
        \onslide<6-|handout:1>{s.t. ${\dsectionc^{i}}\restriction_{\opensetc_i\cap \opensetc_j} = {\dsectionc^{j}}\restriction_{\opensetc_i \cap \opensetc_j}$ for $\opensetc_i, \opensetc_j \in \opensetc$,}
        \onslide<7-|handout:1>{\\there exists $\dsectionc \in \sheafc(\opensetc)$ such that $\dsectionc\restriction_{\opensetc_i} = {\dsectionc^{i}}$} 
    \end{block}      
\end{frame}

@@

\begin{frame}<presentation:1|handout:1>{Example: Scatter Plot}
    \begin{figure}
        \includegraphics[scale=.1]{figures/math/push_pull_scatter.png}
    \end{figure}
\end{frame}

\begin{frame}<presentation:1|handout:1>{Example: Line Plot}
    \begin{figure}
        \includegraphics[scale=.1]{figures/math/push_pull_line.png}
    \end{figure}
\end{frame}

\begin{frame}<presentation:1|handout:1>{Example: Image}
    \begin{figure}
        \includegraphics[scale=.1]{figures/math/push_pull_image.png}
    \end{figure}
\end{frame}

\begin{frame}<presentation:1|handout:1>{Example: Heatmap}
    \begin{figure}
        \includegraphics[scale=.1]{figures/math/push_pull_heat.png}
    \end{figure}
\end{frame}

\begin{frame}<presentation:1|handout:1>{Example: Sphere}
    \begin{figure}
        \includegraphics[scale=.1]{figures/math/push_pull_sphere.png}
    \end{figure}
\end{frame}

@@

\begin{frame}<presentation:1-|handout:1->
    \frametitle<1|handout:1>{$\textcolor{homset}{Hom}_{\gbasec}(\sheaf_{\gbasec, \vindexpullc\dtotalc}, \sheaf_{\gbasec,\gtotalc}) = \textcolor{homset}{Hom}_{\dbasec}(\sheafc_{\dbasec, \dtotalc}, \sheafc_{\dbasec, \vindexpushc\gtotalc})$}
    \frametitle<2|handout:2>{Data Space: $\vartistc_{\dbasec}: \sheafc_{\dbasec, \dtotalc} \textcolor{artist}{\Rightarrow} \sheafc_{\dbasec, \vindexpushc\gtotalc}$}
    \frametitle<3|handout:3>{Display Space: $\vartist_{\gbasec}: \sheafc_{\gbasec, \vindexpullc\dtotalc} \textcolor{artist}{\Rightarrow} \sheafc_{\gbasec, \gtotalc}$}
    \frametitle<4|handout:4>{Artist: $\vartistc: \dsectionc \mapsto \gsectionc$}

    \onslide*<1,4|handout:1,4>{
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement=\&]
          \onslide*<1|handout:1>{\sheafc_{\gbasec, \gtotalc}} 
          \onslide*<4|handout:4>{\cgamma{\opensetgc}{\gtotalc\restriction_{\opensetgc}}}
          \onslide*<1,4|handout:1,4>{\arrow[rr, "\textcolor{functor}{\vindexpush}", color=functor]}  
          \& \& 
          \onslide*<1|handout:1>{\sheafc_{\dbasec, \vindexpushc\gtotalc}}
          \onslide*<4|handout:4>{\cgamma{\opensetc}{\vindexpushc \gtotalc\restriction_{\opensetc}}}
          \\
          \& \& \\
          \onslide*<1|handout:1>{\sheafc_{\gbasec, \vindexpullc\dtotalc}}
          \onslide*<4|handout:4>{\cgamma{\opensetgc}{\vindexpullc \dtotalc\restriction_{\opensetgc}}}
          \onslide*<1|handout:1>{\arrow[uu, "\vartistc_{\gbasec} \in \textcolor{homset}{Hom}_{\gbasec}", color=homset]}
          \onslide*<4|handout:4>{\arrow[uu, "\vartistc_{\gbasec}", color=artist]}
          \&  \& 
          \onslide*<1|handout:1>{\sheafc_{\dbasec, \dtotalc}}
          \onslide*<4|handout:4>{\cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}}}
          \onslide*<1,4|handout:1,4>{\arrow[ll, "\textcolor{functor}{\vindexpull}", color=functor]} 
          \onslide*<1|handout:1>{\arrow[uu, "\vartistc_{\dbasec} \in \textcolor{homset}{Hom}_{\dbasec}"', color=homset]}
          \onslide*<4|handout:4>{\arrow[uu, "\vartistc_{\dbasec}"', color=artist]}
          \onslide*<1|handout:1>{\arrow[lluu, "\vartistc \in \textcolor{homset}{Hom}_{\dbasec,\gbasec}"' description, dashed, color=homset]}
          \onslide*<4|handout:4>{\arrow[lluu, "\vartistc"' description, color=artist]}
        \end{tikzcd}
    \end{equation*}}

    \onslide*<2|handout:2>{
        \begin{equation*}
            \begin{tikzcd}[ampersand replacement=\&]  
                    \&  \& 
                    \sheafc_{\dbasec, \dtotalc} 
                    \arrow[rr, "\vartistc_{\dbasec}", Rightarrow, color=artist] \& \& 
                    \sheafc_{\dbasec, \vindexpushc\gtotalc}  \\
                    \opensetc_1\& \& 
                    \cgamma{\opensetc_1}{\dtotalc\restriction_{\opensetc_1}}
                    \arrow[dd, "\iota^*"', color=set] 
                    \arrow[rr, "\vartistc_{\opensetc_1}", color=artist] \& \& 
                    \cgamma{\opensetc}{\vindexpushc\gtotalc\restriction_{\opensetc_1}} 
                    \arrow[dd, "\iota^*", color=set] \\
                    \& \& {} 
                    \arrow[rr, "\vartistc_{\sheafc}", dotted, color=artist] \& \& {} \\
                    \arrow[uu, "\iota" description, hook, color=base] 
                    \opensetc_2 \& \& 
                    \cgamma{\opensetc_2}{\dtotalc\restriction_{\opensetc_2}}
                    \arrow[rr, "\vartistc_{\opensetc_2}", color=artist] \& \& 
                    \cgamma{\opensetc}{\vindexpushc\gtotalc\restriction_{\opensetc_2}} \\
                    \& \& 
                    \cgamma{\opensetc}{\dtotalc\restriction\opensetc} \& 
                    \opensetc 
                    \arrow[r, "\sheafc_{\dbasec,\vindexpushc\gtotalc}", maps to, color=sheaf] 
                    \arrow[l, "\sheafc_{\dbasec, \dtotalc}"', maps to, color=sheaf] \& 
                    \cgamma{\opensetc}{\vindexpushc\gtotalc\restriction\opensetc}
            \end{tikzcd}                    
        \end{equation*}}

>>>>

\begin{frame}<presentation:0|handout:0>
    \frametitle{Functor $\textcolor{functor}{\bm{F}}: \textcolor{source}{\mathcal{C}} \rightarrow \textcolor{target}{\mathcal{D}}$}
\begin{columns}
    \column{.39\textwidth}
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement = \&, ]
            \onslide*<1-|handout:1>{\textcolor{source}{c}} 
            \onslide*<1-|handout:1>{\arrow[d, "f"', shift right=0, color=source]} 
            \onslide*<3-|handout:1>{\arrow[r, "F", color=functor, maps to]} \& 
            \onslide*<2-3|handout:0>{\textcolor{target}{d}}
            \onslide*<4-|handout:0>{\textcolor{target}{F(c)}} 
            \onslide*<0|handout:1>{\textcolor{target}{F(c)=d}} 
            \onslide*<2|handout:0>{\arrow[d, shift right=0, color=target]}
            \onslide*<3-|handout:0>{\arrow[d, "F(f)", shift right=0, color=target]}
            \onslide*<0|handout:1>{\arrow[d, "F(f)", shift right=3, color=target]} \\
            \onslide*<1-|handout:1>{\textcolor{source}{c^{\prime}}} 
            \onslide*<3-|handout:1>{\arrow[r, "F"', color=functor, maps to]}\& 
            \onslide*<2-3|handout:0>{\textcolor{target}{d^{\prime}}}
            \onslide*<4-|handout:0>{\textcolor{target}{F(c^{\prime})}}
            \onslide*<0|handout:1>{\textcolor{target}{F(c^{\prime})= d^{\prime}}}                    
        \end{tikzcd}
    \end{equation*}
    \column{.59\textwidth}
    \begin{alertblock}<5-|handout:1>{composition}
        \begin{align*}
            \textcolor{functor}{F}(\textcolor{source}{g}) \circ  \textcolor{functor}{F}(\textcolor{source}{f}) = \textcolor{functor}{F} (\textcolor{source}{g}\circ \textcolor{source}{f})
        \end{align*}
    \end{alertblock}
    \begin{alertblock}<6-|handout:1>{identity}
        \begin{align*}
            \textcolor{functor}{F}(\textcolor{source}{id_c}) = \textcolor{target}{id}_{\textcolor{functor}{F}(\textcolor{source}{c})}
        \end{align*}
    \end{alertblock}
\end{columns}
\end{frame}

\subsubsection{Natural Transforms}
\begin{frame}<presentation:0|handout:0>
    \frametitle{Natural Transformation $\textcolor{nattran}{\alpha}: \textcolor{functor}{F} \textcolor{nattran}{\Rightarrow} \textcolor{functor}{G}$}
    \adjustbox{scale=3, center}{
        \begin{tikzcd}[ampersand replacement=\&]
            \& {} \arrow[dd, "\alpha" , Rightarrow, shorten=1.5em, color=nattran] \&             \\
          \textcolor{source}{\mathcal{C}} \arrow[rr, "F", bend left, color=functor] \arrow[rr, "G"', bend right, color=functor] \& \& \textcolor{target}{\mathcal{D}} \\
            \& {} \&            
          \end{tikzcd}}
\end{frame}

\begin{frame}<presentation:0|handout:0>
    \frametitle{Natural Transformation $\textcolor{nattran}{\alpha}: \textcolor{functor}{F} \textcolor{nattran}{\Rightarrow} \textcolor{functor}{G}$}
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement=\&]  
                \&  \& 
                \textcolor{target}{d_s} \& 
                \textcolor{source}{c} 
                \arrow[r, "G", maps to, color=functor] 
                \arrow[l, "F"', maps to, color=functor] \& 
                \textcolor{target}{d_t} \\
                \textcolor{source}{c_1} 
                \arrow[dd, "f" description, color=source] \& \& 
                \textcolor{target}{F(c_1)} 
                \arrow[dd, "F(f)"', color=target] 
                \arrow[rr, "\alpha_{c_1}", color=nattran] \& \& 
                \textcolor{target}{G(c_1)} 
                \arrow[dd, "G(f)", color=target] \\
                \& \& {} 
                \arrow[rr, "\alpha_{f}", dotted, color=nattran] \& \& {} \\
                \textcolor{source}{c_2} \& \& 
                \textcolor{target}{F(c_2)} 
                \arrow[rr, "\alpha{c_2}", color=nattran] \& \& 
                \textcolor{target}{G(c_2)} \\
                \& \& 
                \textcolor{target}{F} 
                \arrow[rr, "\alpha", Rightarrow, color=nattran] \& \& 
                \textcolor{target}{G}                        
        \end{tikzcd}                    
    \end{equation*}
\end{frame}

@@

\begin{frame}<presentation:1-|handout:1>
    \frametitle{Presheaf Functor: $\sheafc: \mathcal{C}^{op} \textcolor{sheaf}{\rightarrow} \setc $}
    \begin{columns}
    \column{0.29\textwidth}
    \begin{tikzcd}[ampersand replacement=\&, row sep=huge]
        \onslide*<8-|handout:1->{\dfiberc}
        \onslide*<8-|handout:1->{\arrow[r, hook]} \& 
        \onslide*<1-|handout:1->{\dtotalc}
        \onslide*<1-|handout:1->{\arrow[d, "\pi"']} \\
           \& 
        \onslide*<1-|handout:1->{\dbasec}
        \onslide*<2-|handout:1->{\arrow[u, "\dsectionc \in \cgamma{\dbasec}{\dtotalc}"', bend right, pos=.5]}
        \end{tikzcd}
    \column{0.69\textwidth}
        \begin{tikzcd}[ampersand replacement = \&, column sep=small]
            \onslide*<2,5-|handout:0>{{\cgamma{\opensetc_1}{\dtotalc\restriction_{{\opensetc_1}}}}} 
            \onslide*<3-4|handout:0>{{\cgamma{\opensetc_1}{\dtotalc\restriction_{{\opensetc_1}}}}\in Ob(\setc)}
            \onslide*<0|handout:1>{\Ob(\setc) \ni {\cgamma{\opensetc_1}{\dtotalc\restriction_{{\opensetc_1}}}}}
            \&  
            {} \& 
            \onslide*<5-|handout:1>{{\cgamma{\opensetc_2}{\dtotalc\restriction_{\opensetc_2}}}} 
            \onslide*<6-|handout:1>{\arrow[ll, "\iota^*"', hook', color=set]} \\\& \&\\
            \onslide*<2|handout:0>{\opensetc_1 \subset \dbasec}
            \onslide*<3-4|handout:0>{\opensetc_1 \in Ob(\mathcal{\dbasec}^{\textcolor{base}{op}})}
            \onslide*<5-|handout:0>{\opensetc_1}
            \onslide*<0|handout:1>{Ob(\mathcal{\dbasec}^{\textcolor{base}{op}}) \ni \opensetc_1} 
            \onslide*<4-|handout:0>{\arrow[uu, "\sheafc_{\dbasec, \dtotalc}", maps to, color=sheaf]}
            \onslide*<0|handout:1>{\arrow[uu, "\sheafc_{\dbasec, \dtotalc}", maps to, color=sheaf, shift right = 10]}
            \onslide*<6-|handout:1>{\arrow[rr, "\iota"', hook, color=base]} \&   
            \onslide*<7-|handout:1>{\arrow[uu, "\sheafc_{\dbasec, \dtotalc}" description, maps to, color=sheaf]} \& 
            \onslide*<5-|handout:1>{\opensetc_2} 
            \onslide*<5-|handout:1>{\arrow[uu, "\sheafc_{\dbasec, \dtotalc}"', maps to, color=sheaf]}                   
            \end{tikzcd}
    \end{columns}
    \begin{center}
        \begin{alertblock}<7-|handout:1>{stalk}
            \begin{align*}
                \sheafc_{\dbasec, \dtotalc}\restriction_{\dbasepointc}\coloneqq \lim\limits_{\opensetc\ni \dbasepointc} \Gamma(\opensetc, \dtotalc\restriction_{\opensetc}) \\
                 \dfiberc_{\dbasepointc} \subset  \sheafc_{\dbasec, \dtotalc}\restriction_{\dbasepointc}
            \end{align*}
        \end{alertblock}

        \begin{alertblock}<8-|handout:1>{germ}
            %germ  is tau at limit, \tau(k) \in germ
            \begin{align*}
                \dsectionc(\dbasepointc) \in \sheafc_{\dbasec, \dtotalc}\restriction_{\dbasepointc}
            \end{align*}
        \end{alertblock}
    \end{center}
\end{frame}

\begin{frame}<presentation:1-|handout:1>{Sheaves on Bundles}
    A sheaf is a presheaf that satisfies the following two axioms\cite{bakerMathsSheaf}\\
    \begin{block}<2-|handout:1>{locality}
        \onslide<3-|handout:1>{
        given $\opensetc = \bigcup\limits_{i\in I} \opensetc_i$ and $\dsectionc^{a}, \dsectionc^{b} \in \sheafc(\opensetc)$,}
        \onslide<4|handout:1>{\\
        if $\dsectionc^{a}\restriction_{\opensetc_i} = \dsectionc^{b}\restriction_{\opensetc_i}$ for each $\opensetc_i \in \opensetc$}
        \onslide<4|handout:1>{then $\dsectionc^{a} = \dsectionc^{b}$}
    \end{block} 
    \begin{block}<5-|handout:1>{gluing} 
         given $\dsectionc^{i} \in \sheafc(\opensetc_i)$
        \onslide<6-|handout:1>{s.t. ${\dsectionc^{i}}\restriction_{\opensetc_i\cap \opensetc_j} = {\dsectionc^{j}}\restriction_{\opensetc_i \cap \opensetc_j}$ for $\opensetc_i, \opensetc_j \in \opensetc$,}
        \onslide<7-|handout:1>{\\there exists $\dsectionc \in \sheafc(\opensetc)$ such that $\dsectionc\restriction_{\opensetc_i} = {\dsectionc^{i}}$} 
    \end{block}      
\end{frame}

@@

\begin{frame}<presentation:0|handout:0>{Example: Scatter Plot}
    \begin{figure}
        \includegraphics[scale=.1]{figures/math/push_pull_scatter.png}
    \end{figure}
\end{frame}

\begin{frame}<presentation:0|handout:0>{Example: Line Plot}
    \begin{figure}
        \includegraphics[scale=.1]{figures/math/push_pull_line.png}
    \end{figure}
\end{frame}

\begin{frame}<presentation:0|handout:0>{Example: Image}
    \begin{figure}
        \includegraphics[scale=.1]{figures/math/push_pull_image.png}
    \end{figure}
\end{frame}

\begin{frame}<presentation:0|handout:0>{Example: Heatmap}
    \begin{figure}
        \includegraphics[scale=.1]{figures/math/push_pull_heat.png}
    \end{figure}
\end{frame}

\begin{frame}<presentation:0|handout:0>{Example: Sphere}
    \begin{figure}
        \includegraphics[scale=.1]{figures/math/push_pull_sphere.png}
    \end{figure}
\end{frame}

@@

\begin{frame}<presentation:1-|handout:1->
    \frametitle<1|handout:1>{$\textcolor{homset}{Hom}_{\gbasec}(\sheaf_{\gbasec, \vindexpullc\dtotalc}, \sheaf_{\gbasec,\gtotalc}) = \textcolor{homset}{Hom}_{\dbasec}(\sheafc_{\dbasec, \dtotalc}, \sheafc_{\dbasec, \vindexpushc\gtotalc})$}
    \frametitle<2|handout:2>{Data Space: $\vartistc_{\dbasec}: \sheafc_{\dbasec, \dtotalc} \textcolor{artist}{\Rightarrow} \sheafc_{\dbasec, \vindexpushc\gtotalc}$}
    \frametitle<3|handout:3>{Display Space: $\vartist_{\gbasec}: \sheafc_{\gbasec, \vindexpullc\dtotalc} \textcolor{artist}{\Rightarrow} \sheafc_{\gbasec, \gtotalc}$}
    \frametitle<6|handout:6>{Artist: $\vartistc: \dsectionc \mapsto \gsectionc$}

    \onslide*<1,8|handout:1,8>{
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement=\&]
          \onslide*<1|handout:1>{\sheafc_{\gbasec, \gtotalc}} 
          \onslide*<8|handout:4>{\cgamma{\opensetgc}{\gtotalc\restriction_{\opensetgc}}}
          \onslide*<1,8|handout:1,4>{\arrow[rr, "\textcolor{functor}{\vindexpush}", color=functor]}  
          \& \& 
          \onslide*<1|handout:1>{\sheafc_{\dbasec, \vindexpushc\gtotalc}}
          \onslide*<8|handout:4>{\cgamma{\opensetc}{\vindexpushc \gtotalc\restriction_{\opensetc}}}
          \\
          \& \& \\
          \onslide*<1|handout:1>{\sheafc_{\gbasec, \vindexpullc\dtotalc}}
          \onslide*<8|handout:4>{\cgamma{\opensetgc}{\vindexpullc \dtotalc\restriction_{\opensetgc}}}
          \onslide*<1|handout:1>{\arrow[uu, "\vartistc_{\gbasec} \in \textcolor{homset}{Hom}_{\gbasec}", color=homset]}
          \onslide*<8|handout:4>{\arrow[uu, "\vartistc_{\gbasec}", color=artist]}
          \&  \& 
          \onslide*<1|handout:1>{\sheafc_{\dbasec, \dtotalc}}
          \onslide*<8|handout:4>{\cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}}}
          \onslide*<1,8|handout:1,4>{\arrow[ll, "\textcolor{functor}{\vindexpull}", color=functor]} 
          \onslide*<1|handout:1>{\arrow[uu, "\vartistc_{\dbasec} \in \textcolor{homset}{Hom}_{\dbasec}"', color=homset]}
          \onslide*<8|handout:4>{\arrow[uu, "\vartistc_{\dbasec}"', color=artist]}
          \onslide*<1|handout:1>{\arrow[lluu, "\vartistc \in \textcolor{homset}{Hom}_{\dbasec,\gbasec}"' description, dashed, color=homset]}
          \onslide*<8|handout:4>{\arrow[lluu, "\vartistc"' description, color=artist]}
        \end{tikzcd}
    \end{equation*}}

    \onslide*<2-6|handout:2>{
        \begin{equation*}
            \begin{tikzcd}[ampersand replacement=\&]  
                    \&  \& 
                    \onslide*<6|handout:2>{\sheafc_{\dbasec, \dtotalc}} 
                    \onslide*<6|handout:2>{\arrow[rr, "\vartistc_{\dbasec}", Rightarrow, color=artist]} \& \& 
                    \onslide*<6|handout:2>{\sheafc_{\dbasec, \vindexpushc\gtotalc}}  \\
                    \onslide*<4-6|handout:2>{\opensetc_1}\& \& 
                    \onslide*<3-6|handout:2>{\cgamma{\opensetc_1}{\dtotalc\restriction_{\opensetc_1}}}
                    \onslide*<5-6|handout:2>{\arrow[dd, "\iota^*"', color=set]} 
                    \onslide*<3-6|handout:2>{\arrow[rr, "\vartistc_{\opensetc_1}", color=artist]} \& \& 
                    \onslide*<3-6|handout:2>{\cgamma{\opensetc}{\vindexpushc\gtotalc\restriction_{\opensetc_1}}} 
                    \onslide*<5-6|handout:2>{\arrow[dd, "\iota^*", color=set]} \\
                    \& \& {} 
                    \onslide*<5-6|handout:2>{\arrow[rr, "\vartistc_{\sheafc}", dotted, color=artist]} \& \& {} \\
                    \onslide*<4-6|handout:2>{\arrow[uu, "\iota" description, hook, color=base]} 
                    \onslide*<4-6|handout:2>{\opensetc_2} \& \& 
                    \onslide*<3-6|handout:2>{\cgamma{\opensetc_2}{\dtotalc\restriction_{\opensetc_2}}}
                    \onslide*<3-6|handout:2>{\arrow[rr, "\vartistc_{\opensetc_2}", color=artist]} \& \& 
                    \onslide*<3-6|handout:2>{\cgamma{\opensetc}{\vindexpushc\gtotalc\restriction_{\opensetc_2}}} \\
                    \& \& 
                    \onslide*<2-6|handout:2>{
                    \cgamma{\opensetc}{\dtotalc\restriction\opensetc} \& 
                    \opensetc 
                    \arrow[r, "\sheafc_{\dbasec,\vindexpushc\gtotalc}", maps to, color=sheaf] 
                    \arrow[l, "\sheafc_{\dbasec, \dtotalc}"', maps to, color=sheaf] \& 
                    \cgamma{\opensetc}{\vindexpushc\gtotalc\restriction\opensetc}}
            \end{tikzcd}                    
        \end{equation*}}

    \onslide*<7|handout:3>{
        \begin{equation*}
            \begin{tikzcd}[ampersand replacement=\&]  
                    \&  \& 
                    \sheafc_{\gbasec, \vindexpullc\dtotalc} 
                    \arrow[rr, "\vartistc_{\gbasec}", Rightarrow, color=artist] \& \& 
                    \sheafc_{\gbasec, \gtotalc}  \\
                    \opensetgc_1\& \& 
                    \cgamma{\opensetgc_1}{\vindexpullc\dtotalc\restriction_{\opensetgc_1}}
                    \arrow[dd, "\iota^*"', color=set] 
                    \arrow[rr, "\vartistc_{\opensetgc_1}", color=artist] \& \& 
                    \cgamma{\opensetgc}{\gtotalc\restriction_{\opensetgc_1}} 
                    \arrow[dd, "\iota^*", color=set] \\
                    \& \& {} 
                    \arrow[rr, "\vartistc_{\sheafc}", dotted, color=artist] \& \& {} \\
                    \arrow[uu, "\iota" description, hook, color=base] 
                    \opensetgc_2 \& \& 
                    \cgamma{\opensetgc_2}{\vindexpullc\dtotalc\restriction_{\opensetgc_2}}
                    \arrow[rr, "\vartistc_{\opensetgc_2}", color=artist] \& \& 
                    \cgamma{\opensetgc}{\gtotalc\restriction_{\opensetgc_2}} \\
                    \& \& 
                    \cgamma{\opensetgc}{\vindexpullc\dtotalc\restriction\opensetgc} \& 
                    \opensetgc 
                    \arrow[r, "\sheafc_{\gbasec,\gtotalc}", maps to, color=sheaf] 
                    \arrow[l, "\sheafc_{\gbasec, \vindexpullc\dtotalc}"', maps to, color=sheaf] \& 
                    \cgamma{\opensetc}{\gtotalc\restriction\opensetgc}
            \end{tikzcd}                    
        \end{equation*}
    }
    \onslide<8|handout:4>{
        \begin{alertblock}{pull data section \dsectionc\ over graphic space $\gbasepointc \in \gbasec$}
            \begin{equation*}
                \vindexpullc\dsectionc(\gbasepointc) = \dsectionc(\vindexc(\gbasepointc)) = \dsectionc(\dbasepointc)
            \end{equation*}
        \end{alertblock}
        \begin{alertblock}{push graphic \gsectionc\ section over data space $\dbasepointc \in \dbasec$}
            \begin{equation*}
                \vindexpushc\gsectionc(\dbasepointc) = \gsectionc\restriction_{\vindexprec(\dbasepointc)} = \gsectionc(\gbasepointc) \forall \gbasepointc \in \vindexprec(\dbasepointc)
            \end{equation*}
        \end{alertblock}
        }
\end{frame}
